---
title: "EMPTY_Correlational_Data_Analysis"
author: "SURV400"
format: docx
editor: visual
---

## The Paper

Nisbet, E., Ortiz, M., Miller, Y., & Smith, A. (2011). The “bin Laden”
effect: How American public opinion about Muslim Americans shifted in
the wake of Osama bin Laden’s death. *School of Communication, Ohio
State University.*

In the late 2000s, a researcher at Ohio State was conducting research on
perceptions of Muslims in the US. On 1 May 2011 at 11:30 PM, then
President Obama announced the death of Osama bin Laden. Recognizing the
unique timestamp this represented, the researchers decided to continue
the study, somewhat artificially with two groups: perceptions before and
after bin Laden's death. Participants were measured on a battery of
constructs including stereotype endorsement against Muslims and support
of restrictions of Muslim civil liberties.

For all variables, higher scores indicated higher levels of the
construct. These data are not the original ones collected in the
study—they were simulated to produce similar results. The analyses we do
will not necessarily emulate the ones in the paper.

Understanding potential reasons why one may endorse limiting Muslim's
civil liberties is critical in the effort to eliminate Islamophobia (and
understanding/eliminating hate toward other groups).

## The Variables

**BINLADEN:** Whether they participated *before* bin Laden was announced
dead (0) or after (1).

**STEREO:** A self-report measure of the endorsement of stereotypes.
(e.g., How much do you associate Tolerance vs. Fanaticism with Muslim
Americans?) Four items scaled 1-5. Total: Average.

**MCIVIL:** A self-report measure of one's support for the restriction
of Muslim civil liberties (e.g., Please rate your agreement with the
statement "All Muslims in the US should carry an ID card."). Five items
scaled 1-5. Total: Average.

**AGE:** The participant's age (standardized).

**IDEO:** Political ideology (higher = conservative).

**SEX:** 0 = female, 1 = male

For all constructs, higher values = greater levels of construct.

## The Analysis

We are going to fit a model to the data with their participation group
(before/after bin Laden's death; BINLADEN) as the predictor and their
endorsement of the restriction of Muslim's civil liberties as the
outcome (MCIVIL).

### Load the Required Packages

We need to read in [**ggplot2**]{.underline} and
[**jtools**]{.underline}.

```{r}

```

### Read in the Data

If you're working on Jupyter, this is in the same folder as the file so
you won't need the file path.

```{r}

```

### Generate Descriptive Statistics

Use the summary command.

```{r}

```

### Visualize the Data

What visualization would be appropriate for a dichotomous predictor and
continuous outcome?

**Answer:**

```{r}
ggplot(data = bl, aes(x = as.factor(binladen), y = mcivil)) +
  geom_boxplot() + 
  labs(x = "Condition (0 = Before Death, 1 = After Death", y = "Restriction of Civil Liberties") + 
  jtools::theme_apa()
```

How do the assumptions look?

-   Linearity:

-   Homogeneity of variance:

-   Normality of residuals: If you want, you can check this in the
    "Model" section using the command hist(resid(model_name))

### Fit the Model to the Data

What correlation coefficient should you run? (Note: The command in R is
the same.)

**Answer:**

```{r}
# run the analysis between the binladen and mcivil variables
cor.test()
```

What are the results?

**Answer:**

### Exploratory Data Analysis

Run the code below if you want to explore the relationship between other
variables in the dataset. You can also test out other relationships
you're interested in! (Or just ignore; the code below will render just
fine.)

```{r}
# exploratory data analysis
ggplot(data = bl, aes(x = as.factor(binladen), y = stereo)) +
  geom_boxplot() + 
  labs(x = "Condition (0 = Before Death, 1 = After Death", y = "Stereotype Endorsement") + 
  jtools::theme_apa()
cor.test(bl$binladen, bl$stereo)

ggplot(data = bl, aes(x = mcivil, y = stereo)) +
  geom_point() + 
  geom_jitter() + 
  labs(x = "Restriction of Civil Liberties", y = "Stereotype Endorsement") +
  jtools::theme_apa()

# run the correlation between the mcivil and stereo variables
cor.test(bl$mcivil, bl$stereo)
```

## End of script
